\bf A Model-Based Scheduling Framework for Enhancing Robustness

### 2019-04-26 paper.tex
Draft complete sections 2 and 3 and start on Results section 4.  Add illustration material for bias visualizations.

The present work is a meta-approach that is motivated by the desire to apply
existing scheduling approaches within a framework that is realistic and
operationally practical.  In terms of scheduling taxonomy, we assume a dynamic
scheduling formulation in which the computational jobs (we call them workflows)
are modeled as directed acyclic graphs, i.e., the tasks of a workflow have
precedence constraints.  Furthermore, each workflow (not individual tasks) is
endowed with a deadline.

Our framework, illustrated in Figure \ref{fig:platform}, consists of one
centralized scheduler and two instances of the computational platform.  The
first instance, denoted as the actual platform, represents the actual machines
(virtual or physical) upon which the actual workflows' tasks are to be executed.
The second instance of the platform, denoted as the model platform, is a
mathematical and/or simulated model representation of the actual platform.  The
scheduler component makes decisions about what machine each task is to be
executed on and when (at or after all the tasks precedence constraints are
satisfied) that execution should begin.  The scheduler makes use of a scheduling
algorithm, which requires some model of the workflows' tasks' requirements.
Scheduling decisions are implemented by a task assigner particular to the
platform, model or actual.

\begin{figure}
	\begin{center}
		\includegraphics[angle=-90,width=0.5\textwidth]{figures/PlatformDiagram.pdf}
	\end{center}
	\caption{Block diagram illustrating proposed framework.}
	\label{fig:platform}
\end{figure}

Much past research has focused on the scheduler component of Figure
\ref{fig:platform}; building schedulers to achieve enhanced performance and/or
robustness.  This is often achieved by focusing on the modeled workflow's
rquirements information provided to the scheduler.  In addition to modeling
requirements, our framework also emphasizes modeling of the platform resources
through the model platform component, providing additional opportunities for
research and improvement.  Such improvements can be realized by building more
accurate models or by making use of feedback from the actual platform to correct
the model platform, indicated by the dashed line of Figure \ref{fig:platform}.

Development and evaluation of static schedules, and schedulers, make use of the
components below the dotted line to build a schedule (set of scheduling
decisions for where and when each task should be executed).  That static
schedule is then used by the actual task assigner component, e.g., via a lookup
table, in a running system like that represented above the dotted line.  Also,
for scheduling algorithms that require training, or offline optimization of
parameters, the same components below the dotted line would be used prior to
deployment of the algorithm in the scheduler of a live system, represented
by the components above the dashed-dotted line.

In the ideal case that the model components match the behavior of the
corresponding actual components, feedback from the actual platform is
unnecessary. Realistically, however, the model components will have deviations
(or errors) in comparison to the actual components with how they
model the tasks' requirements and the availability of platform resources.  This
leads to erroneous information being presented to the scheduler that can be
summarized as two interrelated types.  First, task requirement error results in
inaccurate information about resource load in the model platform, which is
utilized by the scheduler.  Because all scheduling algorithms must fundamentally
determine when to schedule additional tasks on already-loaded resources versus
when to delay starting new tasks until some already-running tasks complete and
the load of the resources lightens (increasing its efficiency), an algorithm
given wrong information about resource load will generally make poor
decisions.

The second type of error the model may exhibit is in the representation of
how much work a task requires to be completed before the task is considered
finished.  When a model's error causes a task's work requirement to be
underestimated, it can lead the scheduling algorithm to assign additional
work to the resource modeled as now having a lightened load.  In this scenario
the error compounds if the algorithm assigns new tasks to the resource because
the additional load causes the atual system's resource to become even less
efficient, further diverging the model from the actual system and causing the
task erroneously modeled as finished to take even longer to finish in the
actual system.  It is also possible that the model for a task overestimates
the task's work requirement in which case the model of the resource remains
loaded while the actual system's resource may be idle.

To counteract the effect of the model diverging from the actual system in
terms of knowledge of which tasks are running, the model may be improved
using feedback from the actual system regarding task completion.  A simple
implementation of this feedback in practice is to instrument the actual system
to provide periodic information about the running tasks on each system
resource.  However, this can cause the model to `lag' behind the actual system
if modeled tasks are not considered completed until a periodic check reveals
its actual system counterpart is no longer executing.  Because scheduling
algorithms make decisions once the state of the system changes in response to
tasks finishing, the aforementioned `lag' may be avoided by having the actual
system provide event-based feedback upon completion of each task.  This latter
`event-driven' approach is adopted in our framework.

\section{Use of Biasing}
\label{sec:Biasing}

This section presents simulated results of the outcomes of scheduling algorithms
whose decisions are made based on a model platform of the (simulated) actual
system in which error is introduced in one aspect of the workflows' tasks'
requirements.  It is shown that by using actual task completion events (fed back
from the actual platform) to correct inaccuracies present in the model
platform, all scheduling algorithms analyzed become very robust to errors in the
tasks' requirements considered.

All simulations were performed using simulator software developed for
previous research \cite{costmin} and made publically available as open source
\cite{soasim}.  As in \cite{costmin} workflows are defined as a directed
acyclic graph where graph nodes represent the computational tasks which are
individually schedulable to execute on one of the platform's available machines.
Graph edges represent precedence constraint where one task must complete
execution before the connected task is able to be scheduled and begin
execution.  In every simulation a scheduling algorithm
is used to schedule tasks from arriving workflows of one of three types, as
also defined in \cite{costmin}: small workflows representative of simple
interactive application jobs, medium workflows representative of web services
jobs, and large workflows representative of large-scale batch-oriented jobs.
Various workflow and task characteristics are summarized in Table
\ref{tab:params}.

\begin{table}
	\begin{tabular}{|l|c|c|c|}
		\hline
		\textbf{Parameter}	& \textbf{Small}	& \textbf{Medium}	& \textbf{Large} \\
		\hline
		Total tasks				& [5,16]	& [10,72]	& [45,800] \\
		Potential Task Parallelism	& [1,2]	& [2,3]		& [5,20] \\
		Task CPU cycles (work)	& [1,2.5]	& [10,50]	& [50,175] \\
		Task CPU utilization	& [0.5,1]	& [0.5,1]	& [0.5,1] \\
		Task memory footprint	& [0.05,0.15] & [0.05,0.1] & [0.05,0.1] \\
		\hline
	\end{tabular}
	\caption{Table of basic workflow (DAG) sizes and tasks' requirements by
		workflow type.}
	\label{tab:params}
\end{table}

As part of the simulation studies the model workflows are given task
requirements where the tasks' amount of CPU cycles ($C_M$) to be completed has
an error term applied to it with respect to the actual value ($C_A$).
This error term parameter $X$ is varied between experiments from 0.001 to 0.9.

\begin{equation}
\begin{split}
C_M & \leftarrow (1+x)C_A \\
x & \in [-X,X]
\end{split}
\end{equation}

\noindent The values for $x$ drawn from $[-X,X]$ assume a uniform distribution.

As with \cite{costmin} all simulations used a simulated platform of 16 machines
with the same resource capacities: $4$ CPUs and a normalized memory capacity of
$1.0$.  From Table \ref{tab:params}, then, each task would consume between half
and all of a single CPU and between $5\%$ and $15\%$ (for small workflows, or
$10\%$ for medium and large) of total memory.  For all numeric results for
$10\%$ for medium and large) of total memory.  Platform machine efficiency was
simulated the same as in \cite{costmin} where cumulative CPU load of all
executing tasks on a machine, $\ell_c$, resulted in an effiency, $e_c$ given in
Eq. \ref{eq:cpueff}.  Memory effiency, $e_m$, based on cumulative memory
load of all executing tasks, $\ell_m$, is given in Eq. \ref{eq:memeff}.
The combined efficiency, $e = e_c e_m$, represents the amount of work
accomplished on each executing task per unit of time.

\begin{equation}
\label{eq:cpueff}
e_c = \begin{cases}
	1, ~~~~~~~~\ell_c < 4 \\
	(4/\ell_c), ~~\ell_c \ge 4
\end{cases}
\end{equation}

\begin{equation}
\label{eq:memeff}
e_m = \frac{10}{10 + \frac{1}{(1/\ell_m) - 1}}
\end{equation}

For all numeric results for
performance the value presented is an averaged value across ten simulations
where the workflows and tasks were the same but a unique random error term,
$x$, was used for each model task's required CPU cycles.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_LowError.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms with no error (vertical
		bars) and with 0.1\% error applied to the model of the workflow
		requirements (line graphs).  In this scenario, task completion event
		feedback was \textbf{not} employed to correct the model platform.}
	\label{fig:noloss-lowerror-nofeedback}
\end{figure*}

@@

Figure \ref{fig:noloss-lowerror-nofeedback} shows the performance of scheduling
algorithms and the significant performance impact that even a small amount of
error has.  In this figure as with prior research, performance is depicted
visually as a histogram of the number of workflows completed in intervals based
on their normalized tardiness (the time difference between the completion and
the target deadline normalized by on-time completion time of the workflow).
In this representation a normalized tardiness of 0 represents a workflow that
completed exactly at its deadline, negative values represent workflows completed
before their deadline, and positive values those completed late.

The histogram bars of Figure \ref{fig:noloss-lowerror-nofeedback} represent the
performance of scheduling algorithms under the ideal circumstance of no error
in the model (i.e., the model platform perfectly predicts and represents the
resources required by a task and its execution completion time).  These
histogram bar results demonstrate how CMSA with either of the two
cost functions (Sigmoid or Quadratic) completes the largest majorities of
workflows ahead of their deadline.  The PLLF (proportional least laxity first)
algorithm completes workflows up to 4 times later (as a proportion of the
ideal finish time) than the deadline. The FCFS (first-come, first-serve)
algorithm performs relatively poorly with workflows completing far later than
their deadline because it is oblivious to deadlines and therefore often will
put off scheduling tasks of a recently-arrived workflow with a `tight' deadline
by prioritizing a less-recently arrived workflow despite its deadline being
further into the future and possibly more relaxed.

The lines graphed in Figure \ref{fig:noloss-lowerror-nofeedback} represent the
same algorithms' histogram of workflow completion in the presence of 0.1\% error
in the model platform.  As depicted, one algorithm (CMSA algorithm optimizing
the cost based on a Sigmoid cost function) maintains roughly the same
performance in the presence of this small model error, as without it.  All three
other algorithms exhibit a dramatic loss in performance, i.e., a shift of many
workflows completing ahead of or shortly after their deadline to completing
many times over later than their deadline.  In this scenario, completion events
were \textbf{not} employed to correct the model platform.

\begin{table}
       \begin{center}
       \begin{tabular}{lllll}
\textbf{Error, }$X$ & \textbf{CMSA}	& \textbf{CMSA}				& \textbf{FCFS}				& \textbf{PLLF} \\
		& \textbf{(Quad)}			& \textbf{(Sig)}			&							& \\
0.0		& \cellcolor{red! 6}16.54	& \cellcolor{green!9}1.77	& \cellcolor{red!28}38.49	& \cellcolor{red!28}38.72 \\
0.001	& \cellcolor{red!20}30.52	& \cellcolor{green!9}1.92	& \cellcolor{red!51}61.39	& \cellcolor{red!40}50.96 \\
0.005	& \cellcolor{red!24}34.75	& \cellcolor{green!9}1.84	& \cellcolor{red!49}59.48	& \cellcolor{red!42}52.39 \\
0.01	& \cellcolor{red!20}30.86	& \cellcolor{green!7}2.99	& \cellcolor{red!50}60.35	& \cellcolor{red!39}49.39 \\
0.05	& \cellcolor{red!18}28.87	& \cellcolor{green!1}8.99	& \cellcolor{red!53}63.60	& \cellcolor{red!39}49.54 \\
0.1		& \cellcolor{red!22}32.11	& \cellcolor{red! 5}15.60	& \cellcolor{red!50}60.77	& \cellcolor{red!42}52.65 \\
0.5		& \cellcolor{red!24}34.34	& \cellcolor{red!14}24.96	& \cellcolor{red!42}52.85	& \cellcolor{red!45}55.68 \\
0.9		& \cellcolor{red!22}32.93	& \cellcolor{red!16}26.12	& \cellcolor{red!44}54.36	& \cellcolor{red!48}58.64 \\
       \end{tabular}
       \caption{Percent of workflows late for four scheduling algorithms
			across various amounts of error in the model platform.  Completion
			events were \textbf{not} employed to correct the model platform.}
       \label{tab:perclate}
       \end{center}
\end{table}

Table \ref{tab:perclate} lists the value of percent of all workflows completed
late (after their deadline) as a single performance metric for the scheduling
algorithms across various amounts of the error term, $X$.  This metric (percent
late workflows) is useful in comparing the impact of increasing error on the
performance of each scheduling algorithm.  Like Figure
\ref{fig:noloss-lowerror-nofeedback}, it illustrates how CMSA (with sigmoid cost
function) is robust to small error, whereas the other algorithms are not.  It
also shows that while the performance of CMSA (Sig) degrades as error increases,
the other three algorithms maintain nearly a constant level of even poorer
performance with any amount of error.  These results show how some algorithms
(CMSA with Sigmoid cost function) can be relatively robust (at least with
respect to this performance metric) for small amounts of error but how all
algorithms eventually perform poorly when using a model platform that fails to
reasonably represent the actual system.

The model task requirement with respect to the amount of CPU cycles each task
requires has a compounding effect when the model system declares, erroneously,
that a task has completed (ahead of the actual system) and thus the scheduler
determine to begin execution of an additional task that increases the system
resource load in the actual system and slows the progression toward completion
even further.  Intuitively, this compounding error is most likely the reason
for such a dramatic decrease in overall scheduler performance for the three
affected algorithms of Figure \ref{fig:noloss-lowerror-nofeedback}.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_HighErrorWithoutModelFinishEvents.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing relative
		performance of scheduling algorithms with no error (vertical bars) and
		with 90\% error applied to the model of the workflow requirements
		(line graphs).  In this scenario, task completion event feedback
		\textbf{was} employed to correct the model platform.}
	\label{fig:noloss-higherror-nomodel}
\end{figure*}

The strategy proposed in this paper is to incorporate feedback from the actual
platform for task completions as an event-based trigger for updating the
model platform and allowing the scheduler to schedule new tasks.  Figure
\ref{fig:noloss-higherror-nomodel} depicts results of the performance of
scheduling algorithms comparable with Figure
\ref{fig:noloss-lowerror-nofeedback} except that the error introduced in the
model is much higher (90\%, instead of 0.1\%) and the model platform uses task
completion events from the actual platform (instead of relying on the model
platform estimates of task completions).  Given that the line graphs match
much more closely to the vertical bars than in Figure
\ref{fig:noloss-lowerror-nofeedback}, this illustrates how even for large
model error the incorporation of actual platform task completion feedback
increases the robustness of all four scheduling algorithms.  The CMSA (Sig)
algorithm which was robust for small amounts of error, as well as the other
three algorithms which were not robust even for the smallest amount of error
studied (0.1\%) all achieve nearly the same level of performance (i.e. shape
of histogram) as with having a perfect, no-error model.

@@

In this paper we introduced a framework for understanding and evaluating
scheduling algorthms' performance and robustness with
respect to error in tasks' resource requirements.  This framework
incorporates a model of the actual system in which errors and uncertainties can
be represented.  Through simulation studies we examined the performance of four
scheduling algorithms and the impact of error in the model system upon their
performance.  While the CMSA algorithm (using a sigmoid cost function) had some
degree of robustness, i.e. it was able to achieve similar performance in the
presence of very small error, all algorithms exhibited poor performance with
even moderate amounts of error present in one dimension of the model workflows
requirements (CPU cycles required for the tasks).

We also introduced and simulated the notion of incorporating feedback from
the actual system back into the model system.  Through simulation studies we
showed how all algorithms can benefit from feedback of task completion events
and thus become relatively robust to even substantial error in the model
system.

In the present paper, we assumed that tasks' completion events are detected
and fed back in order to `correct' the model platform.  Under this
assumption, the model completely relies on actual completion events being
fed back.  Future work will consider the possibility in which partial feedback
(of some) completion events are available and fed back to the model.  This
`partial feedback' assumption may be more practical than the complete feedback
used in this paper in situations where there would be significant overhead
instrumenting the actual system so as to feed back each and every completion
event.  In such cases, taking small samplings of completion events from the
actual system would be more practical. Finally, future work will also
investigate the effect of non-uniform error and/or error distributions without
an expected value of $0$.

>>>>

The present work is an extension to previous work \cite{pdpta18} in which a
model-based approach to dynamically scheduling tasks from DAGs (called
workflows) was introduced.  Four scheduling algorithms were tested in a
simulation environment \cite{soasim} given the same 24-hour simulated period
of arriving workflows ranging in size from 5 tasks up to 800.  Each workflow
had a known, predetermined deadline and scheduling algorithms were evaluated
based both on the number of workflows completed before their deadline and the
distribution of workflow counts completed at various normalized proportions
past their deadline (e.g., workflows up to 100\% late relative to the amount
of time between their arrival and deadline).

Scheduling algorithms are used to determine from a given queue of tasks
ready to begin executing (i.e. tasks of arrived workflows that have no
precedence constraints or whose precedent tasks have all completed) both
when the task should begin executing and on which machine of the platform.
Unlike some scheduling research, tasks are permitted to executing concurrently
with other tasks on the same machine which increases machines' overall load
on resources such as CPU and memory and thereby slows the rate of work on each
executing task.  Original work in \cite{pdpta09} details this non-linear
degradation of rate of work (efficiency) due to concurrent task execution.

Figure \ref{fig:platform} illustrates the various components and general
flow of information within the model-based approach to executing and evaluating
scheduling algorithms.  Whereas the modeled tasks' requirements (CPU load,
required number of CPU cycles, and memory load) may contain errors relative to
the true values of those tasks, the model platform may diverge from the
actual platform in terms of which tasks are completed and which are still
executing.

\begin{figure}
	\begin{center}
		\includegraphics[angle=-90,width=0.5\textwidth]{figures/PlatformDiagram.pdf}
	\end{center}
	\caption{Block diagram illustrating model-based framework from
		\cite{pdpta18}.}
	\label{fig:platform}
\end{figure}

All four studied scheduling algorithms were shown to be sensitive to
even small amounts of error in modeled tasks.  Each scheduling algorithm
exhibited a decreased percent of workflow completed ahead of their deadline
with the smallest amount of error studied.  For three of the scheduling
algorithms the decrease was substantial, but relatively equal, regardless of
the amount of error.  For the fourth scheduling algorithm, the decrease was
less severe overall and was propotionate to the amount of error.  The
fourth algorithm was thus declared to be somewhat robust to small amounts of
error (less than 0.5\%) but ultimately, like all three others, was not
robust for errors of 1\% or greater.

The main result of \cite{pdpta18} showed that incorporating feedback of
task completions from the actual platform to the model platform thereby
preventing the model platform from modeling a task completing before the
actual task completed dramatically increased robustness of all scheduling
algorithms for even errors up to 90\% (the highest amount studied).  Figure
\ref{fig:underestimating} illustrates why the model platform underestimating
the requirements of a task and thereby modeling it as completed ahead of the
actual task can be so detrimental.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figures/UnderestimatedErrorEffect_ModelTaskWork.pdf}
		\includegraphics[width=0.5\textwidth]{figures/UnderestimatedErrorEffect_ActualTaskWork.pdf}
	\end{center}
	\caption{Illustrating the disconnect due to error such that model task
		requirements underestimate actual task requirements and the model
		task finishes ahead of the actual task.}
	\label{fig:underestimating}
\end{figure}

In Figure \ref{fig:underestimating} two tasks, $t_1$ and $t_2$, both have
the same amount of CPU cycles, $C$, required for their completion.  In the
top half is the modeled platform's view of time in which task $t_1$ begins
executing first and when it completed, $t_2$ is scheduled to immediately
begin executing.  However, because the modeled requirements of $t_1$ were
an underestimate of the actual $t_1$'s requirements, when the model of
$t_1$ finishes and $t_2$ is scheduled to begin, the actual platform is not
yet finished with $t_1$ and thus must work concurrently on $t_1$ and $t_2$
for some time until the actual $t_1$ task does complete.  This causes both
$t_1$ and $t_2$ to have actual completion times later than the modeled
completion times because of the unintentionally-overallocated resources of
the machine executing the tasks.  By extension, if another task, say $t_3$,
were to be scheduled to begin after $t_2$ finishes this problem could compound
because $t_2$'s actual completion would delayed by concurrent execution with
$t_1$ and further delayed by concurrent execution with $t_3$.

The previous example illustrates why allowing the model to platform to
inform scheduling algorithms when tasks are complete and machines are
idle (or less loaded) in the presense of error which may underestimate tasks'
true requirements can be so detrimental.  With feedback of every task's
completion from the actual platform the modeled completion times of tasks
may be safely ignored.  However, complete feedback of all tasks' completion
may be impractical in a live system, or may simply be cost-prohibitive.
This paper thus seeks to address the question of whether partial feedback
of tasks' completion times may be sufficient to achieve some level of
robustness to model error.  In addition, based specifically on the
knowledge of the underestimating problem illustrated prior, in Section
\ref{sec:Biasing} that follows a specific approach to counteracting
that problem by biasing model task requirements is proposed.  Results of
both partial feedback and biasing are presented in Section \ref{sec:Results}.

\section{Biasing Model Requirements}
\label{sec:Biasing}

As illustrated in Figure \ref{fig:underestimating}, if the model task
requirements are an underestimate of the actual task's requirements then
scheduling algorithms may schedule future tasks to begin executing
unintentionally-concurrent with other tasks, delaying their completion.
However, if the model is known to have error which may underestimate
task requirements, then the model task requirements could simply be
biased by increasing its value in order to reduce (or ideally, eliminate)
the probability that it underestimates the actual task requirements.
In this section three proposed strategies for biasing model task
requirements are proposed.

The simplest form of biasing would be to add a constant value to each
task requirement.  If the maximum magnitude of error for which a model
task requirement may underestimate the actual task requirement is known,
then that value would be the ideal bias constant value because it would
eliminate the model from ever underestimating task requirements but
bound the worst overestimate to the smallest amount possible for such a
constant value biasing strategy.  Practically, the maximum error magnitude
is unlikely to be known, though because it is the most ideal circumstance
for biasing it is included here and in simulated results of Section
\ref{sec:Results}.  The equation for a simple constant bias value, $C$,
addition to each model task requirement, $\hat{X}$, to yield a biased
model task requirement, $\hat{X^b}$, is given in Eq.
\ref{eq:cbias}.

\begin{equation}
\hat{X^b} \xleftarrow{c} \hat{X} + C
\label{eq:cbias}
\end{equation}

A more practical approach biasing model task requirements is to assume a bound,
not on the magnitude of error, but on the fraction or percentage of error.  It
may be possible, for example, through analysis of past executions of tasks and
workflows, to estimate the maximum percentage of error for each model task
requirement, $\hat{X}$, relative to the actual task requirement, $X$.  In other
words it may be practical to estimate that each model task requirement is
within $P\%$ of the actual task requirement.  Although that means $\hat{X}$
may under- or overestimate $X$ by as much as $P\%$, in order to prevent
underestimating we can adjust $\hat{X}$ as in Eq. \ref{eq:pbias}, hereafter
referred to as the proportionate bias strategy.

\begin{equation}
\hat{X^b} \xleftarrow{p} \hat{X} / (1 - P\%)
\label{eq:pbias}
\end{equation}

Although the proportionate bias strategy can effectively eliminate
underestimated model task requirements with a judiciously chosen $P\%$
which may require less knowledge about the nature of the error than choosing
a proper magnitude for the constant bias strategy value, $C$, this relaxed
requirement comes at a price.  Specifically, where the constant bias
strategy increases the maximum overestimate of actual task requirement, $X$
inherent in $\hat{X}$ by $C$, the proportionate bias strategy `stretches'
the distribution of $\hat{X^b}$ and yields a much larger range of
overestimates.  This is illustrated in Figure \ref{fig:cpbias} where the
distribution of an example model value is adjusted according to the constant
and proportionate bias strategies.  For both adjustments, an ideal value of
$C$ and $P$ are shown, though practically an ideal value wouldn't be known
and have to be estimated itself.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Constant.pdf}
		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Proportionate.pdf}
	\end{center}
	\caption{Illustration of probabilities for a model task requirement
		with bound error as a percentage, $P$, of the actual task
		requirement, $X$, and the effect of constant and proportionate
		bias strategies transforming the distribution into
		one that never underestimates the actual term, $X$, given an
		ideal value for $C$ and $P$.  Distribution is assumed to be
		zero-mean and triangular.}
	\label{fig:cpbias}
\end{figure}

In order to achieve a less `stretched' distribution for the biased model task
requirement than the proportionate bias strategy while still maintaining the
need only for an estimated maximum percentage, not magnitude, of error, the
third proposed strategy, known as the simple bias strategy, is given in Eq.
\ref{eq:sbias}.  It fails to eliminate the possibility of underestimating
though it does reduce its propability substantially, but also prevents wildly
overestimating task requirements by decreasing the amount of `stretch' in the
biased term's distribution.  Figure \ref{fig:sbias} illustrates the effect of
the simple bias strategy on the distribution of the biased term.

\begin{equation}
\hat{X^b} \xleftarrow{s} \hat{X} (1 + P\%)
\label{eq:sbias}
\end{equation}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Simple.pdf}
	\end{center}
	\caption{Illustration of probabilities for a model task requirement
		with bound error as a percentage, $P$, of the actual task
		requirement, $X$, and the effect of the simple bias strategy
		transforming the distribution, given an ideal value for $P$.
		Distribution is assumed to be zero-mean and triangular.}
	\label{fig:cpbias}
\end{figure}

@@

All results were collected using simulations performed using simulator software
developed for previous research \cite{costmin} and \cite{pdpta18} and made
publically available as open source \cite{soasim}.  Workflows and task
requirements are the same as those in \cite{pdpta18} as are simulated error
amounts which ranged from $0.1\%$ up to $90\%$ taken from a uniform
distribution.  For all numeric results for performance the value presented is
an averaged value across ten simulations where the workflows and tasks were
identical but a error term applied to model tasks' requirements were unique.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_LowError.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms with no error (vertical
		bars) and with 0.1\% error applied to the model of the workflow
		requirements (line graphs).  Complete feedback of task completion from
		the actual platform was used, but model platform was, due to
		underestimated task requirements, allowed to model tasks as completing
		and subsequenting scheduling algorithms allowed to schedule additional
		tasks to the machine.}
	\label{fig:noloss-nobias-lowerror}
\end{figure*}

Figure \ref{fig:noloss-nobias-lowerror} shows the performance of the four
scheduling algorithms and the significant performance impact that the smallest
amount of error tested has even when complete feedback is available from the
actual platform but the model platform is still allowed to model tasks as
completing early due to underestimates of task requirements. In this figure
as with prior research, performance is depicted visually as a histogram of the
number of workflows completed in intervals based on their normalized tardiness
(the time difference between the completion and the target deadline normalized
by amount of time available to execute the workflow, i.e., the difference of
deadline and arrival time of the workflow). In this representation a normalized
tardiness of 0 represents a workflow that completed exactly at its deadline,
negative values represent workflows completed before their deadline, and
positive values those completed late.

The histogram bars of Figure \ref{fig:noloss-nobias-lowerror} represent the
performance of scheduling algorithms under the ideal circumstance of no error
in the model (i.e., the model platform perfectly predicts and represents the
resources required by a task and its execution completion time).  These
histogram bar results demonstrate how CMSA with either of the two
cost functions (Sigmoid or Quadratic) completes the largest majorities of
workflows ahead of their deadline.  The PLLF (proportional least laxity first)
algorithm completes workflows up to 4 times later (as a proportion of the
ideal finish time) than the deadline. The FCFS (first-come, first-serve)
algorithm performs relatively poorly with workflows completing far later than
their deadline because the algorithm doesn't use deadline information in making
its scheduling decisions.

The lines graphed in Figure \ref{fig:noloss-nobias-lowerror} represent the
same algorithms' histogram of workflow completion in the presence of 0.1\% error
in the model platform.  Due even to this small amount of error, the problem of
underestimating task requirements and overallocating resources, and the nature
of this issue compounding results in all four scheduling algorithms exhibiting
substantially worse performance.  This is illustrated by the reduction to less
than half as many workflow completed before their deadlines (normalized
tardinesses less than 0) compared to the no-error case.  It is also
demonstrated by the large increase of number of workflows completed with a
normalized tardiness of 10 or higher compared to the no-error case.

Therefore, with any level of partial feedback available it is unexpected that
any of these scheduling algorithms would perform better than the case of
complete feedback being available but still allowing modeling of early task
completions due to underestimated task requirements.  However, the use of
model task requirement biasing showed promising results at restoring
performance of the algorithms by eliminating or reducing the likelihood of
the underestimating problem.

@@
